### 2018-03-20 CO749-GraphColoring/assignments/A4.tex
First case of q3

	Let $G$ be a plane graph, let $S$ be a connected subgraph of $G$, and let $L$ be a $5$-list-assignment for $G$. If $G$ is $S$-critical with respect to $L$ then
	$$v(G|S) \leq c(\defi(G|S) - 1),$$
	where $\defi(G|S) = e(G|S) - 3v(G|S).$
\end{theorem}
We will prove the following lemma, under the assumption that a minimum counterexample $G$ has a vertex in $V(G)\backslash V(S)$ with at least three neighbours in $S$.
\begin{lemma}
	Let $G$ be a plane graph with connected subgraph $S$ and let $L$ be a $5$-list-assignment for $G$. If $\phi$ is an $L$-coloring of $S$ that extends to an $L$-coloring of $G$ then
	$$\log_2 E(\phi) \geq (v(G|S) - (c+1)\defi(G|S))/9,$$
	where $E(\phi)$ is the number of extensions of $\phi$ to $G$ and $c$ is the constant of Theorem \ref{th:def}.
\end{lemma}
\begin{proof}
	Suppose not. Let $(G,S,L)$ be a minimum counterexample, minimizing $v(G|S)$. We may assume $G$ has a vertex $v$ in $V(G)\backslash V(S)$ with at least three neighbours in $S$.
	\paragraph{}

>>>>

	Let $G$ be a plane graph, let $S$ be a connected subgraph of $G$, and let $L$ be a $5$-list-assignment for $G$. If $G$ is $S$-critical with respect to $L$ then
	$$v(G|S) \leq c(\defi(G|S) - 1),$$
	where $\defi(G|S) = e(G|S) - 3v(G|S).$
\end{theorem}
We will prove the following lemma, under the assumption that a minimum counterexample $G$ has a vertex in $V(G)\backslash V(S)$ with at least three neighbours in $S$.
\begin{lemma}
	Let $G$ be a plane graph with connected subgraph $S$ and let $L$ be a $5$-list-assignment for $G$. If $\phi$ is an $L$-coloring of $S$ that extends to an $L$-coloring of $G$ then
	$$\log_2 E(\phi) \geq (v(G|S) - (c+1)\defi(G|S))/9,$$
	where $E(\phi)$ is the number of extensions of $\phi$ to $G$ and $c$ is the constant of Theorem \ref{th:def}.
\end{lemma}
\begin{proof}
	Suppose not. Let $(G,S,L, \phi)$ be a minimum counterexample, minimizing $v(G|S)$. We may assume $G$ has a vertex $v$ in $V(G)\backslash V(S)$ with at least three neighbours in $S$. Let $H = S+v$. 
	\paragraph{}
	We first consider the case that $v(G|S) = 1$, i.e. $G = S + v$.
	\begin{align*}
	\frac{v(G|S) - (c+1)\defi(G|S)}{9} &= \frac{1 - (c+1)e(G|S) +3(c+1)}{9} \\
	&\begin{cases}
		=\frac{1}{9}, &\text{if $|N(v)\cap v(S)| = 3$}  \\
		\leq\frac{1-(c+1)}{9} <0, &\text{if $|N(v) \cap V(S)| \geq 4$}	\end{cases}
	\end{align*}
	Since $\phi$ has at least one extension to $G$ if $|N(v) \cap V(S)| \geq 4$ and $\log_2(1) = 0$, and $\phi$ has at least two extensions to $G$ if $|N(v) \cap V(S)| = 3$ (as at least two colors in $v$'s list are not used at neighbours) and $\log_2(2) = 1 > \frac{1}{9}$, the desired bound holds.
	\paragraph{}
	Therefore we may assume that $v(G|S) \geq 2$. Consider the case that $|N(v) \cap V(S)| \geq 4$. Let $\phi'$ be the extension of $\phi$ to $G$, restricted to $H$. Then $\phi'$ is an $L$-coloring of $H$ which extends to $G$. By minimality, 
	$$\log_2 E(\phi') \geq \frac{v(G|H) - (c+1)\defi(G|H)}{9}$$
	Now $v(G|H) = v(G|S) - 1$.
\end{proof}
